Soil Quality

### 2022-03-24 00_soil_report.Rmd
rename

@@

```{r}
p_soil_values_long <- soil_values_long %>% 
  filter(soil_type %in% c("Tundra", "Grassland", "Conifer Forest")) %>% 
  ggplot(aes(x = soil_type, y = `Value`, fill = soil_type)) +
  geom_col() +
  facet_wrap(~`Measurement`, scales = "free_y") +
  scale_fill_futurama() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p_soil_values_long

>>>>

reported_soil_data <- soil_data %>% 
  filter(soil_type %in% c("Tundra", "Conifer Forest", "Grassland"))

@@

```{r data_output}
write_csv(reported_soil_data, file = "data_output/reported_soil_data.csv")
```

```{r summary_plot}
p_soil_values_long <- soil_values_long %>% 
  filter(soil_type %in% c("Tundra", "Grassland", "Conifer Forest")) %>% 
  ggplot(aes(x = soil_type, y = `Value`, fill = soil_type)) +
  geom_col() +
  facet_wrap(~`Measurement`, scales = "free_y") +
  scale_fill_futurama() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p_soil_values_long
